\input{../Style/default}

% personal data
\firstname{Baojun}
\familyname{Su}
\mobile{13439819854}
\email{freizsu@gmail.com}
%\photo[64pt]{zhaojing.jpg}
\quote{Do everything seriously}

%----------------------------------------------------------------------------------
%                              content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Educational Background}
\cventry{2008 -- 2011}{Master}{Zhejiang University}{Computer Application Technology}{}{}
\cvline{Research Area: }{\small Large scale online learning/text classification/recommender system.}
\cventry{2004 -- 2008}{Bachelor}{Jiangsu University of Science and Technology}{Information and Computing Sciences}{}{}

\section{Work background}
\cventry{2011 -- ~~~~~~~}{Applied Research Engineer}{Netease Youdao}{Beijing}{}{crawler/parser/ranking.}

\section{Technical Ability}
\cvitem{Programming Language}{Java, Python, C, Matlab.}
\cvitem{Operating System}{Linux/Unix,including commands,toolchain,scripts.}
\cvitem{Profiling}{Algorithm profiling, system profiling.}
\cvitem{Large-Scale Data Processing}{Youdao's Map-Reduce/Big Table implementation - Cowork,ODFS etc.}
\cvitem{Data Mining}{Familiar with common models and algorithms of Data Mining, has in-depth study of online learning,text classification and recommender system.}
\cvitem{English}{471 points in CET-6,good English reading and speaking ability.}
\cvitem{Math}{Solid math foundation.}

\section{Projects}
\subsection{Timeliness Web Crawler}
\cvitem{Introduction}{Crawl news from portal sites, forums, microblogs with low latency.}
\cvitem{Timeline}{2011.10 -- 2012.4}
\cvitem{Duty}{Project leader and the only programmer.}
\cvitem{Results}{The rate of timeliness coverage is catching up with Baidu.}
\subsection{Efficiency optimization of DNS Resolve}
\cvitem{Introduction}{The DNS refresh rate is not enough.}
\cvitem{Timeline}{2011.4 -- 2011.6}
\cvitem{Duty}{Project leader and the only programmer.}
\cvitem{Results}{DNS resolve is speeding up by an order of magnitude.}
\subsection{The Application of incremental SVMs in Large-Scale Email Spam Filtering}
\cvitem{Introduction}{National 863 Project}
\cvitem{Timeline}{2008 -- 2009}
\cvitem{Duty}{Project leader,I built the architecture of our TGANG system and implemented
most classiﬁers.}
\cvitem{Results}{The TGANG system is in a leading position internationally both in accuracy
and eﬃciency.}
\subsection{Terminator}
\cvitem{Introduction}{Individual projects,a two-layer ensemble spam filter.}
\cvitem{url}{\url{https://code.google.com/p/terminator/}}
\cvitem{Timeline}{2009 -- 2010}
\cvitem{Results}{ensemble 8 advanced classifiers, can achieve the best results on \emph{All} public datasets.}

\section{Experience}
\subsection{Scholarship}
\cvitem{2009}{Second Prize Scholarship of Zhejiang University.}
\subsection{Open Source}
\cvitem{2010}{Wrote the NSNB spam ﬁlter in Python, which won the ﬁrst place in large-scale spam ﬁltering
competition of Eights Symposium of Search Engine and Web Mining. Now NSNB is open
sourced at \url{http://code.google.com/p/nsnb}.}
\subsection{Publications}
\cvlistitem{Baojun Su, Congfu Xu. Not so naive online Bayesian spam filter. In: Proceedings of the 21st conference on Innovative Application of Artificial Intelligence (IAAI 2009), July 14-16, 2009, Pasadena, CA, pages 147-152.}
\cvlistitem{Congfu Xu, Chunliang Hao, Baojun Su. Research on Markov logic networks. Chinese Journal of Software, 2011, 22(8): 1699-1713. (In Chinese with English abstract)}

\section{Self Assessment}
\cvitem{}{I am a quick learner, with rich developing experience and good understanding of
pattern recognition and machine learning.}


% section section_name (end)
% \section{\fs{个人能力}}
% \cvline{\kai{办公软件}}{能熟练使用~Word、Excel、PowerPoint、Photoshop}
% \cvline{\kai{英语水平}}{托业~600~分、英语六级~434~分、良好的口语表达交流以及文献阅读能力}
% \cvline{\kai{软能力}}{善于组织协调活动、语言表达能力强}

% \section{\fs{荣誉}}
% \cvline{2011}{校优秀研究生一等奖学金}
% \cvline{2009}{校优秀党员}
% \cvline{2009}{“抒辉煌盛世，展青春风采”演讲朗诵比赛三等奖}
% \cvline{2006}{组织并参加洛阳师范学院下乡支教活动，获得洛阳市社会实践先进个人称号}

% \section{\fs{科研}}
% \cvline{\kai{项目}}{作为组内核心参与了两项国家自然科学基金项目（No.20771077、）}
% \cvline{\kai{论文}}{四篇~SCI~索引论文，一篇第一作者、两篇第二作者、一篇第三作者}

% \section{\fs{爱好}}
% \cvline{}{兴趣广泛，尤爱读书，听音乐，旅游，擅长并热爱游泳，坚持冬泳}

% \section{\fs{自我评价}}
% \cvline{}{三年的研究生经历，对于学习能力有了更进一步的提高，具有沉稳的学习气质以及积极地学习热情，平时协助导师管理实验室大小事务，具备良好的沟通能力和组织协调能力}

\end{document}


%% end of file `template_en.tex'.
